


---
title: "R markdown presentation test"
author: "Carina Cornesse, Barbara Felderer and Ulrich Krieger"
affiliation: "SFB 884, University of Mannheim"
subtitle: "The subtitle"
date: "20 Februar 2019"
output: 
  slidy_presentation:
    template: slidy_temp.html
      #font_adjustment: +1
    #footer: "Some Footer"
    #logo: SFB_884_logo_transparent.png
    #css: ioslides_custom.css
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

